Revisiting the Bias-Variance Tradeoff of Multi-Task Learning in High Dimensions

### 2020-08-09 arxiv/experiments.tex
update

\vspace{-0.05in}
We validate our  algorithmic insights and then our theory.
In Section \ref{sec_exp_res}, we first show that single-task learning results can help predict positive or negative transfer.
%the single-task based metric on sentiment analysis and ChestX-ray14 datasets.
Second, our proposed incremental training schedule improves the training efficiency of standard multi-task training on sentiment analysis tasks.
%Third, we measure the data efficiency ratio of multi-task learning on six sentiment analysis tasks.
In Section \ref{sec_exp_ab}, we validate our theoretical results.
We further show that when the sample ratio is large, performing the alignment procedure of \cite{WZR20} provides more improvement for MTL.

@@

{\it Sentiment Analysis.} We consider six tasks: movie review sentiment (MR), sentence subjectivity (SUBJ), customer reviews polarity (CR), question type (TREC), opinion polarity (MPQA), and the Stanford sentiment treebank (SST) tasks.
The question is to predict positive or negative sentiment expressed in the text.
We use an embedding layer with GloVe embeddings
followed by an LSTM, MLP or CNN layer proposed by~\cite{lei2018simple}.

@@

{\it ChestX-ray14.} This dataset contains 112,120 frontal-view X-ray images.
There are 14 diseases (tasks) for every image that we would like to predict.
We use densenet121 as the shared module.
%We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
%This dataset is curated where the labels
%We use the CheXNet model from~\cite{chexnet}, which is a 121-layer convolutional neural network on all tasks.

>>>>

We validate our  algorithmic insights and then our theory.
In Section \ref{sec_exp_res}, we first show that single-task learning results can help predict positive or negative transfer.
%the single-task based metric on sentiment analysis and ChestX-ray14 datasets.
Second, our proposed incremental training schedule improves the training efficiency of standard multi-task training on sentiment analysis tasks.
%Third, we measure the data efficiency ratio of multi-task learning on six sentiment analysis tasks.
In Section \ref{sec_exp_ab}, we validate our theoretical results.
We further show that when the sample ratio is large, performing the alignment procedure of \cite{WZR20} provides more improvement for MTL.

@@

{\it Sentiment Analysis.} We consider six tasks: movie review sentiment (MR) \cite{pang2005seeing}, sentence subjectivity (SUBJ) \cite{pang2004sentimental}, customer reviews (CR) \cite{hu2004mining}, question type (TREC) \cite{li2002learning}, opinion polarity (MPQA) \cite{wiebe2005annotating}, and the Stanford sentiment treebank (SST) tasks \cite{socher2013recursive}.
%The question is to predict positive or negative sentiment expressed in the text.
We use an embedding layer with GloVe embeddings \cite{pennington2014glove}
followed by an LSTM, MLP or CNN layer proposed by~\cite{lei2018simple}.

@@

{\it ChestX-ray14.} This dataset contains 112,120 frontal-view X-ray images \cite{chexnet17}.
There are 14 diseases (tasks) for every image that we would like to predict.
We use densenet121 as the shared module \cite{huang2017densely}.
%We treat each label as one task a binary classification problem and formulate it as a 14-task multi-task learning problem.
%This dataset is curated where the labels
%We use the CheXNet model from~\cite{chexnet}, which is a 121-layer convolutional neural network on all tasks.
